Storing messages with multipartite neural cliques

### 2014-07-17 Articles/article.tex
...
....

\documentclass[english,11pt,twocolumn]{article}
\usepackage[utf8]{inputenc}

@@

\usepackage[autolanguage]{numprint}
\usepackage[affil-it]{authblk}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%
%\usepackage[style=numeric,backend=bibtex]{biblatex}
\pagestyle{myheadings}

@@

\setcounter{secnumdepth}{3} %pour la numérotation subsubsection
\setcounter{tocdepth}{3} %pour la numérotation dans la table de matières
\renewcommand{\theenumi}{\roman{enumi})}
\renewcommand{\thepart}{\Alph{part}}
%\renewcommand{\thechapter}{\arabic{chapter}}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\arabic{subsection}}
\renewcommand{\thesubsubsection}{\alph{subsubsection}}

@@

\theoremstyle{definition}
\newtheorem{theoreme}{Theorem}
\renewcommand{\thetheoreme}{\arabic{section}.\arabic{theoreme}}
\providecommand{\keywords}[1]{\textbf{Index terms---} #1}

@@

	\keywords{associative memory, error correcting code, cliques, multipartite cliques, neural networks}

@@

	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and $m = | \mathcal{M} |$. Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or units. Messages are considered independent and identically distributed.

@@

@@

		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all units that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)

@@

		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $w$-th greater element in an array of $n$ elements is $O(n)$ in complexity.

		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$).
		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}[!htb]
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to $S$}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	Since units representing messages are independent (as messages are themselves independent), the probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum is $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$.

@@

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_densite_c8l256a4}
		\caption{Theoretical and empirical densities}
			\label{densiteth}
	\end{figure}

>>>>

\documentclass[english,10pt,twocolumn]{IEEEtran}
\usepackage[utf8]{inputenc}

@@

\usepackage[autolanguage]{numprint}
\usepackage[affil-it]{authblk}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%
%\usepackage[style=numeric,backend=bibtex]{biblatex}
%\pagestyle{myheadings}

@@

\setcounter{secnumdepth}{3} %pour la numérotation subsubsection
\setcounter{tocdepth}{3} %pour la numérotation dans la table de matières
\renewcommand{\theenumi}{\roman{enumi})}
%\renewcommand{\thepart}{\Alph{part}}
%\renewcommand{\thechapter}{\arabic{chapter}}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\arabic{subsection}}
\renewcommand{\thesubsubsection}{\alph{subsubsection}}

@@

\theoremstyle{definition}
\newtheorem{theoreme}{Theorem}
\renewcommand{\thetheoreme}{\arabic{section}.\arabic{theoreme}}
%\providecommand{\keywords}[1]{\textbf{Index terms---} #1}

@@

	%\keywords{associative memory, error correcting code, cliques, multipartite cliques, neural networks}

@@

	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and $m = | \mathcal{M} |$. Messages in $\mathcal{M}$ are stored in a neural network, of $c \cdot l$ units.

@@

	$\tilde{W} = \max_{1\le i \le m} x_i x_i^\intercal$

	$W_{kl} = \bigg \{
  \begin{tabular}{ccc}
  $0$ & if $\exists i\in [1, c ], \, (i-1)c+1 \le k,l \le ic$ \\
  $\tilde{W}_{kl}$ & otherwise 
  \end{tabular}
  $

@@

		We make a small modification the classic retrieving rule to fully exploit the local regularity of the code (constant weight of $a$). We keep activated all units that achieve a score equal or greater than the $w$-th score. (where $w$ is a positive integer parameter)

@@

		%Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $w$-th greater element in an array of $n$ elements is $O(n)$ in complexity.

		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$ as well).
		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}[!htb]
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to $S$}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	Since unit activations are independent (as messages are themselves independent), the probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum is $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$.

@@

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_densite_c8l256a4}
		\caption{Theoretical and empirical densities for a network of 8 clusters, 256 units per cluster and 4 activated units per cluster}
			\label{densiteth}
	\end{figure}
